MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Sparse Model

### 2020-01-24 cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
add code chunk to compute cor between tissues

@@

# Store enrichment results
write.table(enrichment.results, file = 'CMC_ACC_DLPFC_EnrichResults.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ = File('CMC_ACC_DLPFC_EnrichResults.tsv', 
                  name = 'Enrichment Analysis Results (Dx.Tissue)', 
                  parentId = CODE$properties$id)
ENRICH_OBJ = synStore(ENRICH_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
```
```
|  *Results*                                  |  *SynapseID*                     |
|  -----------------------------------------  |   ---------                      |
|  Covariates                                 |  `r COV_OBJ$properties$id`       |
|  Counts (raw)                               |  `r COUNT_OBJ$properties$id`     |
|  Counts (lcpm)                              |  `r LCOUNT_OBJ$properties$id`    |
|  Offset (for gene length and gc content)    |  `r OFFSET_OBJ$properties$id`    |
|  Design Matrix                              |  `r DM_OBJ$properties$id`        |
|  Residual Expression (for network analysis) |  `r nEXP_OBJ$properties$id`      |
|  Differential Expression                    |  `r DEXP_OBJ$properties$id`      |
|  Enrichment Analysis                        |  `r ENRICH_OBJ$properties$id`    |

>>>>

``` {r cor.repeat.measures}
repeated <- COVARIATES %>%
  tidyr::separate(Dx.Tissue, c('Dx','Tissue'), sep = '_') %>% 
  dplyr::group_by(Individual_ID, Tissue) %>% 
  dplyr::summarize(Samples = n()) %>% 
  dplyr::filter(Samples == 1) %>% 
  dplyr::group_by(Individual_ID) %>% 
  dplyr::summarize(multiSample_perTissue = n()) %>% 
  dplyr::filter(multiSample_perTissue == 2)

glue::glue("{length(unique(repeated$Individual_ID))} of {length(unique(COVARIATES$Individual_ID))} have repeat measurements")

quant_cor <- function(count_matrix, metadata, repeated_vec){
  correlations <- tribble(~ iid, ~ cor)
  for (i in repeated_vec){
     samps <- metadata$SampleID[metadata$Individual_ID %in% i]
     cors <- cor(count_matrix[,samps[1]], count_matrix[,samps[2]])
     entry <- tribble(~ iid, ~ cor,
                      as.character(i), cors)
     correlations <- bind_rows(correlations,entry)
  }
  correlations
}

tmp = NEW.COUNTS
tmp[is.na(tmp)] = 0

correlation_tissue <- quant_cor(tmp, METADATA, repeated$Individual_ID)
```

@@

# Store enrichment results
write.table(enrichment.results, file = 'CMC_ACC_DLPFC_EnrichResults.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ = File('CMC_ACC_DLPFC_EnrichResults.tsv', 
                  name = 'Enrichment Analysis Results (Dx.Tissue)', 
                  parentId = CODE$properties$id)
ENRICH_OBJ = synStore(ENRICH_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store correlation between tissues
write.table(correlation_tissue, file = 'CMC_ACC_DLPFC_correlationTissue.tsv', sep = '\t', row.names = FALSE, quote = FALSE)
COR_OBJ = File('CMC_ACC_DLPC_correlationTissue.tsv',
               name = 'Correlation between Tissues, Same Individual',
               parentId = CODE$properties$id)
COR_OBJ = synStore(COR_OBJ, used = ALL_USED_IDs, activityName = activityName,
                   executed = thisFile, activityDescription = acactivityDescription)
synSetAnnotations(COR_OBJ, annotations = all.annotations)
```
```
|  *Results*                                  |  *SynapseID*                     |
|  -----------------------------------------  |   ---------                      |
|  Covariates                                 |  `r COV_OBJ$properties$id`       |
|  Counts (raw)                               |  `r COUNT_OBJ$properties$id`     |
|  Counts (lcpm)                              |  `r LCOUNT_OBJ$properties$id`    |
|  Offset (for gene length and gc content)    |  `r OFFSET_OBJ$properties$id`    |
|  Design Matrix                              |  `r DM_OBJ$properties$id`        |
|  Residual Expression (for network analysis) |  `r nEXP_OBJ$properties$id`      |
|  Differential Expression                    |  `r DEXP_OBJ$properties$id`      |
|  Enrichment Analysis                        |  `r ENRICH_OBJ$properties$id`    |
